Optimal Particle Paths Around Points in $\R^2$ with Constrained Acceleration

### 2013-10-07 particle_definitions.tex

$\theta(t), \phi(t) \in [-\pi, \pi]$. From now on, $\abs{\theta}$ and $\abs{\phi}$ will be used, since there is a symmetry in the system about $\bhat{r}$.

@@

\begin{align}
  \frac{dr(t)}{dt}& = -v(t) \, \cos\paren{\abs{\theta(t)}}\label{eq:r-deriv}\\
  \frac{d\abs{\phi(t)}}{dt}& = \frac{v(t)}{r(t)} \, \sin\paren{\abs{\theta(t)}}\label{eq:phi-deriv}\\
  \frac{d\abs{\theta(t)}}{dt}& = \frac{d\abs{\phi(t)}}{dt} - \frac{a_c(t)}{v(t)}\\
  &= \frac{v(t)}{r(t)} \, \sin\paren{\abs{\theta(t)}} - \frac{a_c(t)}{v(t)}\label{eq:theta-deriv}\\
  \intertext{Applying the chain rule to (\ref{eq:r-deriv})}
  \frac{d}{dt} \frac{dr(t)}{dt}& = -\frac{dv(t)}{dt} \cos\paren{\abs{\theta(t)}} + v(t) \sin\paren{\abs{\theta(t)}} \frac{d\abs{\theta(t)}}{dt}\\
  &\begin{aligned}
    = -\frac{dv(t)}{dt} \cos\paren{\abs{\theta(t)}} &+ \frac{v(t)^2}{r(t)} \sin^2\paren{\abs{\theta(t)}}\\
    &\qquad - v(t) \sin\paren{\abs{\theta(t)}} \frac{a_c(t)}{v(t)}\label{eq:r-deriv-2}
  \end{aligned}
\end{align}

\begin{lemma}
  For a particle, $p$, with bounded centripetal and tangential acceleration, then:

>>>>

$\theta(t), \phi(t) \in [-\pi, \pi]$. From now on, $\abs{\theta(t)}$ and $\abs{\phi(t)}$ will be used, since there is a symmetry in the system about $\bhat{r}$.

@@

\begin{align}
  \frac{dr(t)}{dt}& = -v(t) \, \cos\paren{\abs{\theta(t)}}\label{eq:r-deriv}\\
  \frac{d\abs{\phi(t)}}{dt}& = \frac{v(t)}{r(t)} \, \sin\paren{\abs{\theta(t)}}\label{eq:phi-deriv}\\
  \frac{d\abs{\theta(t)}}{dt}& = \frac{d\abs{\phi(t)}}{dt} - \frac{a_c(t)}{v(t)}\\
  &= \frac{v(t)}{r(t)} \, \sin\paren{\abs{\theta(t)}} - \frac{a_c(t)}{v(t)}\label{eq:theta-deriv}\\
  \intertext{Applying the chain rule to (\ref{eq:r-deriv})}
  \frac{d}{dt} \frac{dr(t)}{dt}& = -\frac{dv(t)}{dt} \cos\paren{\abs{\theta(t)}} + v(t) \sin\paren{\abs{\theta(t)}} \frac{d\abs{\theta(t)}}{dt}\\
  &\begin{aligned}
    = -a_t \cos\paren{\abs{\theta(t)}} &+ \frac{v(t)^2}{r(t)} \sin^2\paren{\abs{\theta(t)}}\\
    &\qquad - v(t) \sin\paren{\abs{\theta(t)}} \frac{a_c(t)}{v(t)}\label{eq:r-deriv-2}
  \end{aligned}
\end{align}

\begin{lemma}\label{lemma:intermediate-theta}
  For a particle, $p$, with bounded centripetal and tangential acceleration, then:
